---
title: "EE_Downward-Causation_Experiment_Data Comparison"
author: "Johannes Haehnlein"
date: "`r Sys.Date()`"
output: html_document
---

# In this R markdown, we test the reliabilty of our data, by comparing both data sets.

# Libraries

```{r}
library(openxlsx) # Used to import and export excel files
library(tidyverse) # Used to load all tidyverse packages
library(lavaan) # Used to perform confirmatory factor analyses
library(psych) # Used to calculate Cronbach's Alpha and ICC values
library(apaTables) # Used to create correlation tables
library(lme4) # Used for multilevel modeling 
library(lmerTest) # Used for multilevel regression adding p-values to the lme4 package
library(lmtest) # For calculating robust standard errors
library(broom) # Used to create tidy data frames with model results
library(broom.mixed) # Used to tidy result objects for multilevel modeling
library(parameters) # Used to augement regression analyses
library(performance) # Used to  obtain R2 for multilevel models
library(knitr) # Used for table creation
library(clubSandwich) # Used for cluster robust standard errors
library(sandwich) # Used for cluster robust standard errors
library(flextable) # Used for table creation
```

# Data

## Read Data

```{r}
data_manual <- read.xlsx("Data_EE Downward Causation_Conjoint_Wave2.xlsx")
```

## Inspect Data

### Code Book

* age = Age of the subject
* gender = Gender of the subject
* education = Highest education grade
* busexp = Years of business experience of the entrepreneur
* compfound = Respondent being an entrepreneur
* amountfound = Amount fo founded companies
* compage = Years since (last) startup foundation
* compact = Ongoing activity of the entrepreneur in his startup
* role = Function of the entrepreneur in his startup
* compcity = city of company headquarters
* amountemp = Amount of employees in the entrepreneurs startup
* pubfund1 = public funding by a funding program in germany
* programpart = Participation in an accleration or incubation program
* startupcenter = Being in located in a startup or technology center
* eecontlik = Conjoint Card 1-8 (Assessment of likelihood to engage in the EE contribution behavior)
* eecontlikrep = Replication Conjoint Card 1-8 (Assessment of likelihood to engage in the EE contribution behavior)
* ee_support_reception = Perceived EE support
* ee_affiliation = Affiliation to the EE
* ee_relationships = Personal Relationship to EE actors
* altruism_potential = Altruistic potential
* positive_outcome_expectation = Expected positive outcome of the activity
* benefit_perception = Perceived benefits of the entrepreneur
* evaluation_scenexp = Experience of the described scenario
* evaluation_scenpract = Practicability of the described scenario
* evaluation_studreal = Realism of the described study
* evaluation_critund = Understandability of decision criteria
* evaluation_fun = Fun factor of the study
* ipfinvx = Intense Positive Feeling towards inventing (4 items)
* ipffndx = Intense Positive Feeling towards founding (3 items)
* ipfdev = Intense Positive Feeling towards developing (3 items)
* esex = Entrepreneurial Self-Efficacy (4 items)
* ic_inv = Identity Centrality inventing
* ic_fnd = Identity Centrality founding
* ic_dev = Identity Centrality developing
* ex_orx = Exchange Orientation (9 items)
* selfintx = Self-Interest (3 items)
* othorix = Other Orientation (3 Items)
* gentrustx = General Trust Scale (6 Items)
* bogusx = Bogus Item 1 & 3
* sudoku = Bogus Item 2
* duration = time to complete survey (min)

### Variable names

```{r}
colnames(data_manual)
```

# Data Preparation for Analysis

## Harmonize Variable Names

```{r}
data_manual <- data_manual |>
  rename_all(.funs = tolower) |> # Convert all column names to lower case
  rename("role" = "function") |> # Convert variable "function" to "role"
  rename("icfnd" = "ic_icfnd") |>
  rename("icdev" = "ic_icdev") |>
  rename("icinv" = "ic_icinv") |>
  rename("pubfund" = "pubfund1") |>
  rename("scenexp" = "evaluation_scenexp") |>
  rename("scenpract" = "evaluation_scenpract") |>
  rename("studreal" = "evaluation_studreal") |>
  rename("critund" = "evaluation_critund") |>
  rename("fun" = "evaluation_fun") |>
  rowid_to_column(var = "respondent_id") # Create id column
```

## Remove effortless responses

In order to ensure data quality, respondents with low survey engagement shall be removed from the sample. To check these effortless respondents, we included three bogus items (attention checks) in our survey. We remove all respondents who failed the bogus. Also we remove respondents, who finished the survey too fast or too slow. Based on the survey's pre-test the estimated completion time was between 12 and 20 minutes. According to this, we will remove all respondents, who completed the survey in less than 8 minutes and in more than 40 minutes.

### Remove failed bogus item responses

```{r}
data_manual <- filter(data_manual, bogus1 == 6) # Remove all respondent failing bogus item 1
data_manual <- filter(data_manual, sudoku == 4) # Remove all respondent failing bogus item 2
data_manual <- filter(data_manual, evaluation_bogus3 == 4) # Remove all respondent failing bogus item 2
data_manual <- filter(data_manual, bogus3 == 4) # Remove all respondent failing bogus item 4
```

### Remove too fast or too slow conducting respondents

```{r}
duration_lower <- 8 # response time lower than 8 minutes
duration_higher <- 40 # response time higher than 40 minutes
```

```{r}
time_out_lower <- data_manual |>
  filter(duration > duration_lower) |>
  nrow()
```

```{r}
time_out_higher <- data_manual |>
  filter(duration < duration_higher) |>
  nrow()
```

```{r}
data_manual <- data_manual |>
  filter(duration >= duration_lower) |>
  filter(duration <= duration_higher)
```

### Sample Size (Wave 1)

```{r}
nrow(data_manual)
```


## Read Data Set 2

```{r}
data_prolific <- read.xlsx("Data_EE Downward Causation_Conjoint_Prolific.xlsx")
```

## Inspect Data

### Code Book

* age = Age of the subject
* gender = Gender of the subject
* education = Highest education grade
* busexp = Years of business experience of the entrepreneur
* compfound = Respondent being an entrepreneur
* amountfound = Amount fo founded companies
* compage = Years since (last) startup foundation
* compact = Ongoing activity of the entrepreneur in his startup
* role = Function of the entrepreneur in his startup
* compcity = city of company headquarters
* amountemp = Amount of employees in the entrepreneurs startup
* pubfund1 = public funding by a funding program in germany
* programpart = Participation in an accleration or incubation program
* startupcenter = Being in located in a startup or technology center
* eecontlik = Conjoint Card 1-8 (Assessment of likelihood to engage in the EE contribution behavior)
* eecontlikrep = Replication Conjoint Card 1-8 (Assessment of likelihood to engage in the EE contribution behavior)
* ee_support_reception = Perceived EE support
* ee_affiliation = Affiliation to the EE
* ee_relationships = Personal Relationship to EE actors
* altruism_potential = Altruistic potential
* positive_outcome_expectation = Expected positive outcome of the activity
* benefit_perception = Perceived benefits of the entrepreneur
* evaluation_scenexp = Experience of the described scenario
* evaluation_scenpract = Practicability of the described scenario
* evaluation_studreal = Realism of the described study
* evaluation_critund = Understandability of decision criteria
* evaluation_fun = Fun factor of the study
* ipfinvx = Intense Positive Feeling towards inventing (4 items)
* ipffndx = Intense Positive Feeling towards founding (3 items)
* ipfdev = Intense Positive Feeling towards developing (3 items)
* esex = Entrepreneurial Self-Efficacy (4 items)
* ic_inv = Identity Centrality inventing
* ic_fnd = Identity Centrality founding
* ic_dev = Identity Centrality developing
* ex_orx = Exchange Orientation (9 items)
* selfintx = Self-Interest (3 items)
* othorix = Other Orientation (3 Items)
* gentrustx = General Trust Scale (6 Items)
* bogusx = Bogus Item 1 & 3
* sudoku = Bogus Item 2
* duration = time to complete survey (min)

### Variable names

```{r}
colnames(data_prolific)
```

# Data Preparation for Analysis

## Harmonize Variable Names

```{r}
data_prolific <- data_prolific |>
  rename_all(.funs = tolower) |> # Convert all column names to lower case
  rename("role" = "function") |> # Convert variable "function" to "role"
  rename("icfnd" = "ic_icfnd") |>
  rename("icdev" = "ic_icdev") |>
  rename("icinv" = "ic_icinv") |>
  rename("pubfund" = "pubfund1") |>
  rename("scenexp" = "evaluation_scenexp") |>
  rename("scenpract" = "evaluation_scenpract") |>
  rename("studreal" = "evaluation_studreal") |>
  rename("critund" = "evaluation_critund") |>
  rename("fun" = "evaluation_fun") |>
  rowid_to_column(var = "respondent_id") # Create id column
```

## Remove effortless responses

In order to ensure data quality, respondents with low survey engagement shall be removed from the sample. To check these effortless respondents, we included three bogus items (attention checks) in our survey. We remove all respondents who failed the bogus. Also we remove respondents, who finished the survey too fast or too slow. Based on the survey's pre-test the estimated completion time was between 12 and 20 minutes. According to this, we will remove all respondents, who completed the survey in less than 8 minutes and in more than 40 minutes.

### Remove failed bogus item responses

```{r}
data_prolific <- filter(data_prolific, bogus1 == 6) # Remove all respondent failing bogus item 1
data_prolific <- filter(data_prolific, sudoku == 4) # Remove all respondent failing bogus item 2
data_prolific <- filter(data_prolific, evaluation_bogus3 == 4) # Remove all respondent failing bogus item 2
data_prolific <- filter(data_prolific, bogus3 == 4) # Remove all respondent failing bogus item 4
```

### Remove too fast or too slow conducting respondents

```{r}
duration_lower <- 8 # response time lower than 8 minutes
duration_higher <- 40 # response time higher than 40 minutes
```

```{r}
time_out_lower <- data_prolific |>
  filter(duration > duration_lower) |>
  nrow()
```

```{r}
time_out_higher <- data_prolific |>
  filter(duration < duration_higher) |>
  nrow()
```

```{r}
data_prolific <- data_prolific |>
  filter(duration >= duration_lower) |>
  filter(duration <= duration_higher)
```

### Sample Size (Wave 1)

```{r}
nrow(data_prolific)
```




Independent Samples T-Test for numeric variables

```{r}


numeric_variables <- c("age", "busexp", "amountfound", "compage", "amountemp", "duration")

t_test_results <- lapply(numeric_variables, function(var) {
    t.test(data_manual[[var]], data_prolific[[var]], var.equal = TRUE)
})


# Apply the function to each variable and create a summary table
t_test_summaries <- sapply(t_test_results, function(test) {
    c(round(test$estimate, 3), p.value = round(test$p.value, 3))
})

t_test_summaries

```

Chi-Square Test of Independence for Binary and Categorical Variables:

```{r}

binary_variables <- c("pubfund", "programpart", "startupcenter")

chi_square_results <- lapply(binary_variables, function(var) {
  # Combine the variables from both datasets
  combined_var <- factor(c(data_manual[[var]], data_prolific[[var]]))
  # Create a group factor to distinguish between datasets
  group_factor <- factor(rep(c("manual", "prolific"), c(nrow(data_manual), nrow(data_prolific))))
  # Perform Chi-Square test
  chisq_test_result <- chisq.test(table(combined_var, group_factor))
  
  return(list(
    chi_sq = chisq_test_result$statistic,
    p_value = chisq_test_result$p.value,
    expected = chisq_test_result$expected
  ))
})

# Display results
chi_square_results

# Initialize an empty data frame for the summary
chi_square_summary <- data.frame(
  Variable = character(),
  Chi_Square = numeric(),
  P_Value = numeric(),
  stringsAsFactors = FALSE
)

# Loop through the results and populate the summary table
for (i in seq_along(chi_square_results)) {
  chi_square_summary <- rbind(chi_square_summary, 
                              data.frame(
                                Variable = binary_variables[i],
                                Chi_Square = chi_square_results[[i]]$chi_sq,
                                P_Value = chi_square_results[[i]]$p_value
                              ))
}

# Print the summary table
print(chi_square_summary)


```

Mann-Whitney U Test for Likert Scale Variables:

```{r}

likert_variables <- c("eecontlike1", "eecontlike2", "eecontlike3", "eecontlike4", "eecontlike5", "eecontlike6", "eecontlike7", "eecontlike8", "eecontlike1rep", "eecontlike2rep", "eecontlike3rep", "eecontlike4rep", "eecontlike5rep", "eecontlike6rep", "eecontlike7rep", "eecontlike8rep")

# Initialize an empty data frame for the summary
mwu_summary <- data.frame(Variable = character(), W = numeric(), P_Value = numeric(), stringsAsFactors = FALSE)

# Perform Mann-Whitney U Test and populate summary table
for (var in likert_variables) {
  test_result <- wilcox.test(data_manual[[var]], data_prolific[[var]])
  mwu_summary <- rbind(mwu_summary, data.frame(Variable = var, W = test_result$statistic, P_Value = test_result$p.value))
}

# Round values for readability
mwu_summary <- mwu_summary %>%
  mutate(W = round(W, 2), P_Value = round(P_Value, 3))

# Print the summary table
print(mwu_summary)

```